Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-03-19 Response/response-1.tex

\cmnt{1} In Section II.B, please provides more justifications for the problem formulation in (6). For example, the Queue weighted sum rate maximization (Q-WSRM) is throughput optimal, i.e., if there exists a scheme which can make all queues stable, then the Q-WSRM can also do this. How about the proposed formulation in (6)? Is it also throughput optimal?

\resp \review{We thank the reviewer for the comment. The Q-WSRM scheme and the proposed schemes are all throughput optimal. It can be seen that the proposed extension Q-WSRME and the JSFRA formulations aim at minimizing the number of backlogged packets in addition to avoiding the over allocation of available resources. The JSFRA formulation using \me{\ell_1} norm as the objective minimizes the number of backlogged packets in a greedy manner at each instant. By increasing the exponent \me{q \rightarrow \infty}, we obtain fair allocation at every transmission instant. We have included the discussions on the average number of backlogged packets at each instant for different arrival rates in Section V-C on page 13, col. 1. We have provided justifications for the problem formulation in (6) and (16) in page 5, col. 1, first paragraph. The equivalence between the Q-WSRM scheme and the \me{\ell_2} norm objective in the JSFRA formulation can be seen easily when the number queue size increases. We have clarified this point in the revised manuscript. Please refer to the first paragraph in Section III-B.}

\cmnt{2} Do the proposed solutions based on (6) achieve better average delay performance than the existing solutions? By the way, in the simulations, you should also add a figure comparing the average delay performance, instead of just comparing the performance metric defined by (6). This will better justify the advantage of the proposed solutions.

\resp \review{
	\begin{itemize}
		\item In the previous manuscript, we primarily focused on evaluating the performance of all schemes by comparing the total number of backlogged packets retained in the system after the current transmission. Since the delay is proportional to the average number of backlogged packets in the system, this implies that the delay performance was indirectly evaluated in the previous manuscript. In addition, the average delay of a particular user can be reduced by controlling the priority factor \me{a_k} in (6a), which affects the resource allocation. We have included this statement in the manuscript in Section II-B after (6). We can also control the delay by changing the exponent used in the objective \me{\ell_q} of the JSFRA problem as discussed in bullet points before Section III.
		\item We considered the residual number of backlogged packets as a performance measure, since we assume only the instantaneous channel state informations and together with the number of backlogged packets, resources can be allocated only for a given instant.
		\item We agree with the reviewer that the delay should be compared directly to justify the advantages of the proposed schemes. In this regard, we have included a new figure to clarify this point. Please refer to Fig. 4 and the associated text in Section V-C. As can be seen, the proposed methods outperforms the existing schemes.
	\end{itemize}
	}

@@

\cmnt{3} In Section III.B, the convergence conditions under Algorithm 1 are not clear. First, you should be more specific about what is the SCA subproblem. Do you mean problem (19)? Second, does the uniqueness of the transmit and receive beamformers mean that the solution of the original problem in (16) is unique, or the solutions of the subproblems in (19) and (20) are unique, respectively?

\resp \review {
	\begin{itemize}
	\item We thank the reviewer for the comment. The convergence analysis has been clearly written in the revised manuscript in Appendix B. The discussions are provided for the convergence of the iterative Algorithm 1, \textit{i.e}, the problem defined in (16). 
	\item The uniqueness of the convex subproblem (20) can be guaranteed by the linear constraint on the transmit precoders in (19), which is susceptible to the transmit precoder phase rotations. On the other hand, the constraint in (16b) is not, since the precoder variable is inside the absolute value operator. Once the algorithm finds a unique set of transmit precoders, all unitary rotations are also valid for the original problem in (16). The uniqueness of the transmit and the receive beamformers are discussed in detail in Appendix B-D.
	\end{itemize}
}

\cmnt{4} It is better to clearly summarize the convergence conditions and results (i.e., does it converge to a stationary point or the optimal solution) for all algorithms in a theorem/proposition.

\resp \review{The discussions on the convergence of the centralized algorithms is provided in Appendix B and for the distributed algorithms in Appendix C. The discussion on the convergence to a stationary point is presented in Appendix B-E.}

@@

\cmnt{5} At the end of Section III, you mentioned that the proposed reduced complexity resource allocation scheme is sensitive to the order in which the subchannels are selected for the optimization problem. Please provide a discussion how to choose this order.

\resp \review{Since the sub-channel wise resource allocation considers each sub-channel at a given time for designing the precoders, the performance of this scheme depend on the selection order of the sub-channels. For instance, to design the precoders for the sub-channel \me{j+1}, we assume the transmit precoders and the rates of all users are evaluated for the sub-channels \me{\{1,2,\dotsc,j\}}. At this point, we have to estimate the number of backlogged packets left over in the system, if the sub-channels \me{\{1,2,\dotsc,j\}} are transmitted with the precoders designed so far. Now, the number of backlogged packets for the \me{\ith{j+1}} sub-channel is given by 
\[\max \Big( Q_k - \sum_{i=1}^j \sum_{l=1}^L t_{l,k,i},0 \Big).\]
Since it depends on the rates of the already evaluated sub-channels \me{\{1,2,\dotsc,j\}}, it is susceptible to the ordering used to determine the precoders in each sub-channels. It is discussed in detail in Section III-D. Note that the performance will be closer to the JSFRA centralized scheme, if we select the best sub-channel ordering through an exhaustive search. In this case, the performance loss is mainly due to the maximum power constraint on each sub-channel.}

@@

\cmnt{6} In the distributed algorithms, it is not clear what exact information is exchanged between the BSs or between the BSs and users. Moreover, the signaling overhead should be analyzed and compared with the centralized solution. The proposed distributed algorithms require exchanging over-the-air signaling or backhaul signaling for many times within each channel coherent time (e.g., from Fig. 2, the distributed algorithm requires 20-30 iterations to converge even when there are only 3 subchannels). I don’t think this is acceptable in practice. Is the signaling overhead of the distributed algorithm really smaller than the centralized algorithm which only requires exchange the CSI between the BSs for once within each channel coherent time?

\resp \review{
	\begin{itemize}
		\item The distributed algorithms are derived for the convex subproblem, which leads to the same stationary point asymptotically as that of the centralized solution, but indeed we would require a large number of iterations for the convergence. In reality, we have to limit the number of iterations required for each distributed algorithm, thereby leading to a point which may not be the same as when the algorithm is allowed to converge. The number of ADMM or primal updates can be controlled by \me{J_{\max}} in the Algorithm 2.
		\item Note that the size of the channel state information depends on the number of transmit antennas. Thus exchanging channels is not efficient when the number of transmit antennas are large. On the other hand, the amount of exchanging interference vector only depends on the number of base stations. In practice, we can limit the primal or ADMM update for few iterations, then the distributed algorithms are still be efficient.
		\item To this end, we have a practical scheme in Section IV-D. Note that in the time-correlated case, it is often also enough to update the precoders once per radio frame. The decentralized schemes are never allowed to converge until the end, it is only important to follow the fading process when \me{J_{\max} = 1}. The performance of the distributed algorithm based on dual decomposition scheme is discussed for the time-correlated fading in Section C of [13] in the revised manuscript, which shows that it is enough for the distributed precoder design to follow the fading process to provide desired performance. The distributed algorithm for the time correlated case is not provided in the current manuscript, since it is not in the scope of the precoder design algorithms considered in this manuscript.
	\end{itemize}
	}

@@

\cmnt{10} Do you have any convergence result for the proposed distributed solution based on the KKT conditions in Section IV.B? It seems that the iterative method to solve the KKT conditions is totally heuristic.

\resp \review{
	\begin{itemize}
		\item The heuristic part is that instead of updating the involved variables sequentially, we allow all the variables to be updated at the same time. Due to this idea, the convergence is not always guaranteed as in standard methods, but we have observed significantly improved convergence results in all numerical examples.
		\item It follows the same points as that of the centralized approach if the algorithm is iterated in the same order, \textit{i.e} the dual variables are allowed to converge before the update of the fixed operating point and the receiver. Here instead we perform the update of the transmit precoders, receive beamformers and the dual variables all at once in each iteration. Thus, we sacrifice the formal convergence for the improved speed of convergence. We have provided additional details on the convergence of the KKT based approach in page 10, col 1, last paragraph.
	\end{itemize}}

\cmnt{11} Since queue is a dynamic system evolving according to (3), it doesn’t make sense to compare the queue deviations at a given time. You should compare average queue deviations in the simulations. Moreover, you should also compare the average delay performance instead of just comparing the performance metric (queue deviations) defined in this paper. Using the queue deviations as the performance metric also needs more justification.

\resp \review{
	\begin{itemize}
		\item We agree with the reviewer comment and is in line with Q.2. Please refer to the response for the comment on delay as the performance metric discusion. 
		\item In accordance with the reviewer comment, we have included Section V-C to discuss the queue deviation over multiple transmission slots. We have presented Fig. 4a by comparing the average number of backlogged packets for different algorithms with various arrival rates and Fig. 4b for the number of backlogged packets at each instant. Note that the question on delay arises when we are considering the resource allocation over certain duration. Since the paper is about the precoder design to minimize the number of backlogged packets at each instant, it may not be a valid performance metric for our objective. 
		\item We agree that delay can be controlled by reducing the number of packets on an average, as we can see from Fig. 4, the proposed algorithm performs better in comparison with the existing schemes in minimizing the average number of backlogged packets. Note that we can also prioritize the users by controlling the variable \me{a_k} in (6a) to address the QoS constraints for a particular user. In addition to that, we can also change the objective to \me{\ell_2} and \me{\ell_{\infty}} norm to address the delay and the fairness implicitly. It is included in Section II-B after (6) and in the itemized listing following (7).
	\end{itemize}}

@@

\cmnt{12} What is “SRA” in the simulation figures?

\resp \review{SRA stands for spatial resource allocation (SRA). It is updated in the revised manuscript in Section III-D.}

\cmnt{13} In the discussion for Fig. 1, you mentioned that JSFRA converge to the optimal point, and all algorithms are Pareto-optimal. Since the problem is non-convex, why these algorithm can find optimal solution or Paretooptimal point?

\resp \review{Since the problem is nonconvex, the JSFRA formulation can find a stationary point upon convergence. The converged point of the JSFRA problem is in fact the stationary point of the original nonconvex problem, which is discussed in Appendix B-E on page 15, col. 2. We have removed the statement mentioning the Pareto-optimal solutions in the discussions on Fig. 1 in the revised manuscript.}

### 2015-03-19 Response/response-2.tex

\review{We would like to thank the reviewer for providing valuable comments.}

\begin{itemize}

\cmnt{1} The logic from (6) to (16) is not clear. The only difference is the two newly introduced NON-CONVEX constraints (16b) and (16c), while the objective function (16a) and the constraint (16d) is the same as (6). The equivalence between (6) and (16) is not straightforward and it is confusing why the reformulation in (16) is beneficial.

\resp \review{The reformulation is required, since the SINR expression in (2) cannot be handled directly in the problem defined in (6). Note that the equality constraint imposed by the SINR expression in (2) is handled by the two explicit inequality constraints (16b) and (16c), which are the under estimator to the original problem in (6). Since the inequalities are used to replace the equality constraint, the objective could be improved by the iterative algorithm and the equality will be achieved after the convergence, thereby having one-to-one mapping at the final solution. We have updated the manuscript to include the details for better clarity on third paragraph in Section III-B.}

@@

\cmnt{2} The authors use the successive convex approximation framework, but the approximate problem proposed by the authors is actually not convex. Inspecting (19), its objective function is the same as in (6), and the non-convexity of (6) comes exactly from the objective function, so (19) is not a convex problem. The same flaw is repeated several times in the approximate problems proposed by the authors.

\resp \review{
	\begin{itemize}
		\item Please note that the objective function in the problem formulation is convex, which can be verified by writing the difference function inside the norm operator in epigraph form. Since the problem in (16) is not jointly convex on the variables \me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n}}, we use alternating optimization (AO) approach by fixing \me{\mvec{w}{l,k,n}} and optimize for \me{\mvec{m}{l,k,n}} as a variable.
		\item Even after fixing \me{\mvec{w}{l,k,n}} as constant, the problem in (16) is nonconvex due to the DC constraint (16b), which is handled by the first order relaxation around some fixed operating point. Once the linear relaxation is performed, the problem in (20) is a convex optimization problem with the variables being \me{\mvec{m}{l,k,n},\gamma_{l,k,n},\beta_{l,k,n}}. The manuscript is updated to illustrate this clearly on the lines following after (19).
	\end{itemize}
}

@@

\cmnt{3} The authors proposed to use block coordinate descent method to solve (16). But as the authors have already pointed out, to apply block coordinate descent method, the constraint sets for different variables should be disjoint (uncoupled), which is however not the case in (16), because receive and transmit precoders (i.e w and m) are coupled in the constraints. It is confusing on its own why the authors made a statement that contradicts the proposed methodology, and the convergence followed is in question.

\resp \review{We thank the reviewer for the pointing out the flaw in the text. We have removed the incorrect statement on the block coordinate descent method with the AO approach on the fourth paragraph in Section III-B after (16). Indeed, due to the coupling of the transmit and the receive precoder variables, we cannot use the standard block coordinate descent method proof for the convergence of the proposed algorithm as pointed out by the reviewer. We have provided a completely rewritten convergence proof in Appendix B. }

@@

\cmnt{4} Regarding the convergence of the SCA, the authors cited [27] for the convergence conditions, but the reference is wrong, because the conditions after the three bullets on page 6 are not mentioned in [27]. In case the authors disagree, please make the citation more specific, for example, specify the theorem/statement/proposition in [27] where those conditions are specified.

\resp \review{We apologize for the inappropriate reference cited in the original manuscript. We have provided a completely rewritten proof on the convergence of the centralized algorithm in Appendix B.}

@@

\cmnt{6} Another comment on reference: to the reviewer's knowledge, the term SCA is never explicitly used in [2]. So please either correct the reference or be more specific (section, theorem, etc.).

\resp \review{We have removed the inappropriate citation of the references.}

\cmnt{7} The authors propose primal decomposition method, ADMM approach to the non-convex problem (19), while their convergence analysis is based on literature that proved convergence for convex problems only, e.g., [13]. So the convergence analysis is not trustworthy.

\resp \review{Please note that the distributed algorithm is performed for the convex subproblem presented in (20) and (28). Since the problem is convex, the distributed approach convergence can be guaranteed under certain conditions. Those are discussed in Appendix C on the convergence analysis for the distributed algorithms.}

@@

\cmnt{8} The length of the paper is too extensive. Some of the reformulations as mentioned in the previous comment can be skipped. Also, Section III.D. is not deeply explained and does not bring additional value to the paper. The implications of ordering the sub-channels for the iterative approach should be carefully studied and extensively explained in a different publication.

\resp \review{We have included the sub-channel wise resource allocation or (SRA) scheme in Section III-D for the completeness. It is presented in the manuscript as an alternative suboptimal approach to perform sub-channel wise distributed precoder design by the centralized controller. We have updated the manuscript with more details for better understanding.  We have also stream-lined the manuscript so that some redundant discussion has been removed here and there. We also improved the grammar and fluency.}

@@

\cmnt{10} In Fig. 1 and Fig. 2, the labels for the system model do not fit with the written description. Additionally, the reference scheme Q-WSRM is not optimal, since it over allocates resources if there are few queued packets. Therefore, it is not interesting for comparison purposes.

\resp \review{We understand the reviewer's concern. We have updated the manuscript to include the descriptions in the text to refer the legends used in the figures. Table 1 is provided for the purpose of insight, since it deals with the SISO scenario with 3 sub-channels and 3 users. }

\cmnt{11} Assuming that Fig. 2 and Fig. 3 where obtained based on the same simulation setup, i.e. user queues, number of transmit and receive antennas and number of base stations, it is not clear why results in Fig. 3 are worse than Fig. 2 when comparing JSFRA. Even more, since the number of sub-channels is larger in Fig. 3, the result seems contradictory.

\resp \review{
	\begin{itemize}
		\item We thank the reviewer for pointing out the issue in the system description for the figures. Please note that the simulation scenario is different for Fig. 2 and Fig. 3 in terms of path loss distribution and the sub-channel numbers.
		\item We have provided different scenario with the centralized algorithm as reference for studying the performance under different system model. The user path loss is distributed uniformly between $[0,-6]$ dB for Fig. 2 and between $[0,-3]$ dB for Fig. 3.
		\item We have updated the manuscript to include these details. In addition, the number of backlogged packets in the system for Fig. 3 is \me{[9,16,14,16,9,13,11,12]} bits. These facts are updated in the revised manuscript on Section V-B third paragraph.
	\end{itemize}
  }

### 2015-03-19 Response/response-3.tex

\cmnt{1} The number of transmitted packets \me{t_k}'s are optimization variables, which should be explicitly stated in the problem formulation of (6), (16), (19), (20) and (26) to avoid confusing.

\resp \review{Please note that the objective function uses \me{v_k =  Q_k - t_k = Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} \log_2(1+\gamma_{l,k,n})} expression instead of including an additional constraint for the transmitted packets using the rate expression and thus \me{t_k} is not a variable. However, in the MSE formulation, we have explicitly stated the optimization variable \me{t_k}, since it is present in the DC constraint (27).}

\cmnt{2} The manuscript states that the inequalities (16b) and (16c) achieve equality at optimality(line 23, page 5). This is not obvious. An easy case to check this statement is that assuming the system has two BS and each BS serves one user. When \me{Q_1=0} and 2nd BS has sufficiently large power, (16b) and (16c) do not hold equality. Rigorous proof is needed if authors stick to this statement.

\resp \review{
	\begin{itemize}
		\item We thank the reviewer for the insightful comment. We have updated the manuscript to include the statement that the proposed approximation in (16b) and (16c) are the under-estimator for the SINR expression in (2) on the third paragraph in Section III-B.
		\item The under-estimator is tight when there is at least one user in each BS that cannot be served by the current transmission as discussed in Appendix A. It has multiple solutions, when the objective is zero even for a single BS. In this case, we can use a regularization term with the total power in the objective to obtain an unique solution. We have discussed the uniqueness of the proposed algorithm in detail in Appendix B-D.
	\end{itemize}
	 }

@@

\cmnt{3} The solution in (21) is obtianed for MMSE, i.e. for 2-norm(q=2). If \me{q=1} or \me{q=\infty}, it is actually an equivalent linear programming problem. Details for this solution should be provided.

\resp \review{We thank the reviewer for the critical comment. Note that the receiver has no explicit relation with the choice of \me{\ell_q} norm used in the objective function. The dependency is implicitly implied by the transmit precoders \me{\mvec{m}{l,k,n}}, which indeed depend on the value of \me{q}. We have modified the text to include this information on the sentence following after (22).}

@@

\cmnt{4} The convergence proof need to be rigorous. The inequality of (23a) is opposite to the reference [28]. Also the statement on uniqueness of the transmit and the receive beamformers are not correct. Although we can choose one antenna to be real value, this does not mean the problem has unique solution!

\resp \review{We agree with the reviewer. Appendix B in the revised manuscript discuss the convergence proof rigorously. The uniqueness is also justified implicitly by the linear approximation performed on the DC constraint (16b), which makes the transmit precoders to be susceptible to the phase rotation. The uniqueness discussions are presented in Appendices B-D.}

@@

\cmnt{5} (25) is generally wrong. (25) only holds when the MSE is minimized(by MMSE receiver) and the snr is the optimized(which is obtained by general eignvalue decompostion). This is clearly stated in the reference [5] and [6]. This can also be easily checked by comparing (25) and (2). Consequently the alternative formulation (26) based on this conclusion is questionable.

\resp \review{
	\begin{itemize}
		\item We agree that the MSE equivalence with the SINR expression is valid only when the receiver is based on the MMSE objective. In our solution based on MSE reformulation, we have used the MMSE receiver irrespective of the \me{\ell_q} norm used in the objective. 
		\item Since the receivers are based on the MMSE objective, the equivalence is valid between the MSE and the SINR expression. Since the transmit precoders are updated in accordance with the objective, the MSE reformulation yields the same solution as the SCA approach based JSFRA scheme presented in Section III-B. It can also be verified from Fig. 1 for \me{\ell_1} objective. We have updated the manuscript to include this comments in the lines following (25) in Section III-C.
	\end{itemize}
	}

@@

\cmnt{6} For ADMM aproach, the determination of the value of \me{\rho} in equation (35a) should be discussed. 1. The numbers of transmitted packets for users  \me{t_k}'s are optimization variables. So they should be explicitly stated in the problem formulation (6), (16), (20) and (26) to avoid confusing.

\resp \review{We agree with the reviewer's concern. We have included reference [11] that discusses on the valid choices of the step size parameter for ADMM. We have included the statement that it depends on the system model under consideration. This information is updated on the manuscript in the lines following after (40).}

### 2015-03-19 Response/response-4.tex

\cmnts{i} - {p. 5, col. 1, rows 27-30: Here you might want to quickly mentioned how one could show the NP-hardness of (16).}

\resp \review{We have included the NP-hardness of the proposed solution by modeling the current problem to solve the \ac{WSRM} formulation, which is known to be NP-hard on the last sentence in Section III-B third paragraph.}

\cmnts{j} - {p. 5, col. 1, row 50: "According to the SCA method...". I am not sure exactly how you define "\_the\_ SCA method"? Clarify or cite the definition.}

\resp \review{We have removed the sentence mentioning the SCA method. We have updated the manuscript to discuss this as SCA approach in the sentences after (17).}

@@

\cmnts{n} - {p. 6, col. 2, rows 8-10: I don't fully understand the reasoning on the relation between the constraint sets in the different iterations. Why is this the case?}

\resp \review{To solve the nonconvex problem (16), we linearize the DC constraint (16b) around a fixed operating point. Since the operating point happens to be the optimal solution from the earlier iteration, the optimal point of the previous iterations is also present in the current feasible set. Therefore, at each iteration, the algorithm finds a better solution or the same compared to the previous solution, which leads to the monotonically decreasing objective. Please refer to Appendix B for more details on the convergence analysis of the centralized algorithm.}

\cmnts{o} - {p. 7, col. 1, row 35: Just because a problem is convex does not mean that it has a unique solution. (Although it seems to me that (26) should have a unique solution.) Is the problem in (26) strictly convex?}

\resp \review{
	\begin{itemize}
		\item We thank the reviewer for the critical comment. It is true that the convex problem does not need to have a unique solution in general. By using Minkowski inequality \me{\|x + y\|_q \leq \|x\|_q + \|y\|_q }, we can see that the JSFRA problem is not strictly convex for all exponents \me{\ell_q} used in the objective function. 
		\item The uniqueness of the solution is obtained due to the linear constraint (19) in the problem formulation (20). Note that the linear constraint (19) is susceptible to the phase rotations on the transmit precoders, whereas any unitary rotations on the transmit precoders still satisfies the original nonconvex constraint (16b). 
		\item When the constraints (19),(20b) and (20d) are all active for all BSs, \textit{i.e}, when the objective is nonzero for all BSs, we obtain a unique set of transmit precoders. On the contrary, it has multiple solutions when the objective is zero even for a single BS. In this case, we can use a regularization term with the total power in the objective to obtain an unique solution. We have discussed the uniqueness of the proposed algorithm in detail in Appendices B-D. It makes the objective strictly convex, therefore, it has a unique minimum.
	\end{itemize}
		}

@@

\cmnts{p} - {Table 1: "backpreassure"}

\resp \review{It is updated in the manuscript in Table I.}

\cmnts{q} - {p. 11, col. 1, row 56: "performances". I'm not sure this is a countable noun.}

\resp \review{We checked the gramatical validity and kept the plural in some cases.}

### 2015-03-19 Report/conclusions.tex
updated nam comments review should be modified
with_markku_corrections

In this paper, we addressed the problem of allocating downlink space-frequency resources to the users in a multi-cell \ac{MIMO} \ac{IBC} system using \ac{OFDM} transmission. The resource allocation is considered as a joint space-frequency precoder design problem since the allocation of a resource to a user is obtained by a non-zero precoding vector. We proposed the \ac{JSFRA} scheme by employing the \ac{SCA} technique to relax the nonconvex constraint by a sequence of convex subsets for designing the precoders to minimize the total number of user queued packets. Additionally, an alternative \ac{MSE} relaxation approach is also proposed by using \ac{SCA} technique to address the nonconvex constraints for a fixed \ac{MMSE} receivers. We then introduced distributed precoder designs for the \ac{JSFRA} problem using primal and \ac{ADMM} methods. Finally, we proposed a practical iterative algorithm to obtain the precoders in a decentralized manner by solving the \ac{KKT} conditions of the \ac{MSE} reformulated \ac{JSFRA} method. The proposed iterative algorithm requires few iterations and limited signaling exchange between the coordinating \acp{BS} to obtain the efficient precoders for a given number of iterations. Numerical results are used to compare the performance of the proposed algorithms with the existing solutions.

>>>>

In this paper, we addressed the problem of allocating downlink space-frequency resources to the users in a multi-cell \ac{MIMO} \ac{IBC} system using \ac{OFDM}. The resource allocation is considered as a joint space-frequency precoder design problem since the allocation of a resource to a user is obtained by a non-zero precoding vector. We proposed the \ac{JSFRA} scheme by relaxing the nonconvex \ac{DC} constraint by a sequence of convex subsets using the \ac{SCA} for designing the precoders to minimize the total number of user queued packets. Additionally, an alternative \ac{MSE} relaxation approach is also proposed by using the \ac{SCA} to address the nonconvex \ac{DC} constraints for a fixed \ac{MMSE} receivers. We also proposed distributed precoder designs for the \ac{JSFRA} problem using primal and \ac{ADMM} methods. Finally, we proposed a practical iterative algorithm to obtain the precoders in a decentralized manner by solving the \ac{KKT} conditions of the \ac{MSE} reformulated \ac{JSFRA} method.  The proposed iterative algorithm requires few iterations and limited signaling exchange between the coordinating \acp{BS} to obtain the efficient precoders for a given number of iterations. Numerical results are used to compare the performances of the proposed algorithms with the existing solutions. The distributed design for the time correlated fading will be considered in future.
